---
title: "H/W Lab#2"
author: "Thakur Prasad Ghimire"
date: "9/21/2021"
output: word_document
---

1.What are the names of the people in your study group?


.Thakur Ghimire 
.Nicholas Alonso 
.Bolina Oxilus 
.Diep luu 
Joel rosas 

2.Write up the results of your Lab 2 work. I don’t want all of your output, please pick the interesting bits (and start thinking about what makes a result interesting?).


```{r setup,include=TRUE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
library(readxl)
```

```{r}
acs2017_ny_data <- read_csv("C:/acs2017_ny_data.RData")
```


```{r}
summary(acs2017_ny_data)
```


#first change the factor back in to a numaber.
```{r}
 
 acs2017_ny$IND_number <- as.numeric(levels(acs2017_ny$IND))[acs2017_ny$IND]
 acs2017_ny$Covid_risk <- ((acs2017_ny$IND_number > 4600) & acs2017_ny$IND_number < 6000) | ((acs2017_ny$IND_number > 8500) & (acs2017_ny$IND_number < 8700))

```



```{r}
group_by<-Covid_risk$EGFIELD%>%
  arrange(desc(Percentage))

```



# Among the degreefield i choose the psychology and fine arts to compare and analyze provided data.
```{r}
Psychology <- acs2017_ny[acs2017_ny$DEGFIELD=='Psychology', ]
Psychology %>% count(Covid_risk, sort = TRUE)
```

```{r}
psychology_by_sex <- fine_arts %>% 
  filter(!is.na(Covid_risk)) %>% 
  group_by(Covid_risk, SEX) %>% 
  summarise(Count=n()) %>%
  mutate(Percentage=Count/sum(Count)*100)

```



```{r}
ggplot(psychology_by_sex, aes(fill=Covid_risk, y=Percentage, x=SEX)) + 
  geom_histogram(position="dodge", stat="identity")


```

```{r}
ggplot(psychology_by_sex, aes(fill=Covid_risk, y=Percentage, x=SEX)) + 
  geom_histogram(position="dodge", stat="identity")

```
```{r}
psychology_by_citizen <- fine_arts %>% 
  filter(!is.na(Covid_risk))%>% 
  group_by(Covid_risk, CITIZEN) %>% 
  summarise(Count=n()) %>%
  mutate(Percentage=Count/sum(Count)*100)


```




```{r}
ggplot(psychology_by_citizen, aes(fill=Covid_risk, y=Percentage, x=CITIZEN)) + 
  geom_histogram(position="dodge", stat="identity")

```

```{r}
fine_arts <- acs2017_ny[acs2017_ny$DEGFIELD=='Fine Arts', ]
fine_arts %>% count(Covid_risk, sort = TRUE)
```
```{r}
fine_arts_by_sex <- fine_arts %>% 
  filter(!is.na(Covid_risk)) %>% 
  group_by(Covid_risk, SEX) %>% 
  summarise(Count=n()) %>%
  mutate(Percentage=Count/sum(Count)*100)


```


```{r}
ggplot(fine_arts_by_sex, aes(fill=Covid_risk, y=Percentage, x=SEX)) + 
  geom_histogram(position="dodge", stat="identity")

```






```{r}
ggplot(fine_arts_by_citizen, aes(fill=Covid_risk, y=Percentage, x=CITIZEN)) + 
  geom_histogram(position="dodge", stat="identity")



```







